Combining information from photometric and spectroscopic data:\\ Don't waste your time in spectrophotometric calibration!

### 2014-07-28 tex/ms.tex
adding figures and captions to ms

@@

We are now left to demonstrate that it is possible to infer the
parameters of interest $\theta$ while marginalizing over the
calibration parameters $\alpha$.  We will apply the methodology for
spectrophotometric calibration described above to \emph{actual,
real} optical spectra of a stellar clusters in M31.  Spectra of star
clusters provide a good test case, as they are less complex than
galaxy spectra (for which it is necessary to model the star formation
history) but are by no means trivial. In this way the key features of
the calibration model and methodology are not obscured.

@@

\begin{figure}[h!]
\caption{Shows the calibrated and uncalibrated spectrum for one
  cluster, along with the uncertainty spectrum and (maybe) the
  calibration vector. \label{fig:data}}
\end{figure}

\begin{table}[h!]
\caption{List all the clusters, and individual exposures.}
\end{table}

@@

Nebular emission lines (which may arise from HII regions around the
clusters or from diffuse ionized gas) and interstellar absorption
lines are modeled as a sum of Gaussians of unknown amplitude $A_\ell$,
all of the same width $\sigma_e$ (which need not be the same as
stellar broadening $\sigma$) and with known central wavelengths
$\lambda_\ell$.  For emission lines the amplitudes are constrained to
be positive, while for interstellar absorption (e.g. Na D and Ca K)
the amplitudes are constrained to be negative. This framework can be
easily extended to include more complex models for the nebular
emission, such as allowing line dependent widths and velocities, and
using Voight profiles for the line shapes.  NB GAUSSIANS ARE A NOT
GREAT APPROXIMATION FOR ABSORPTION LINE SHAPES (GAUSSIAN IN OPTICAL
DEPTH, NOT $\Delta F$)

The final mean model is then given by 
\begin{eqnarray}\label{eq:MeanModel} 
\mu(\theta) &  = & (G_\sigma  \otimes F_{\theta^\prime})(\lambda) +
\sum_{\ell=0}^{N_\ell} S_\ell \\
S_\ell & = & \frac{A_\ell}{\sigma_e\sqrt{2\pi}} \exp(-\frac{(\lambda -
 \lambda_\ell)^2}{2\sigma_e^2})\\
\theta & \equiv & \left[ \{\theta^\prime\}, \sigma, \{A_\ell\}_{\ell=0}^{N_l},
  \sigma_e \right]
\quad ,
\end{eqnarray}
where $G_\sigma$ represents a Gaussian of unit area 
and standard deviation $\sigma$, 
$\otimes$ indicates convolution, 
and the full parameter set $\theta$ now includes
the instrumental wavelength broadening $\sigma$, 
and the dispersion $\sigma_e$ and
amplitudes $A_\ell$ of the $N_l$ nebular and interstellar emission
lines. 
This is the mean model which appears in equation
\ref{eq:SpectroscopicLF}.

@@

We first infer the parameters of interest $\theta$ for a calibrated
spectrum of one of the clusters, using the full YY-band photometry. In
Figure \ref{fig:inferred_spectrum} we show the spectrum resulting
from draws of the parameters $[\theta,\alpha]$ from the posterior
distribution.  This figure also shows the calibrated spectrum on which
the priors were conditioned, and several of the individual components
of the model constructed from each draw.  In Figure
\ref{fig:inferred_spectrum} we also show the residuals between the data
and the draws from the posterior, for both the spectra and the
photometry. In Figure \ref{fig:inferred_params} we show the
marginalized and joint PDFs for the parameters.

@@

\begin{figure}[h!]
\caption{Show, for one cluster, the (un)calibrated spectral data, draws from
  the posterior for the model, and residuals \label{fig:inferred_spectrum}}
\end{figure}

\begin{figure}[h!]
\caption{Show the observed photometric SED and draws from the
  posterior, for one cluster.\label{fig:inferred_sed}}
\end{figure}

@@

\begin{figure}[h!]
\caption{Show the calibration vector and our inference of it? \label{fig:inferred_calib}}
\end{figure}

@@

@@

BDJ INSERT WORDS HERE.  We have demonstrated, using a sample of
stellar clusters in M31, that we can combine photometric and
spectroscopic data in a principled way to infer physical properties.
We do not resort to an arbitrary down-weighting or up-weighting of
certain data. Instead, we explicitly model our uncertain knowledge of
the spectral calibration and infer it along with the physical
properties. For a number of applications this combination of
spectroscopy and photometry reduces the need for spectrophotometric
calibration.  Calibration information, if it exists, can be
incorporated into informative priors on the calibration parameters of
our model.

Our strategy is easily extensible to more complicated models, which
include for example night sky line emission in the spectroscopy,
wavelength calibration.  DISCUSS MORE COMPLICATED COVARIANCE KERNELS,
MULTIPLE KERNELS, etc.  MODEL CHECKING.

@@

Limitations.  The strategy we have advocated has several limitations.
First, it requires a generative model for the spectrum of the object
of interest, and is thus ill-suited to discovery projects.  Second,
care must be taken to avoid absorbing interesting model deficiencies
into the calibration model.  Third, we have made the assumption that
the spectrscopy and the photometry are sampling the same populations.
In practice, differences between spectroscopic and photometric
apertures often mean that the photometry and the spectroscopy are sampling
slightly different physical regions.  The correct response to this
situation is to explicitly model the differences, incorporating prior
information about the spatial variation of physical properties.
Finally, this method is computationally intensive and expensive, since
we are constantly inverting largish matrices.

BDJ misc issues, collected here in case we want to address them and
to keep me from cluttering up the main text: effective aperture
corrections (i.e. we're implicitly assuming photometry and
spectroscopy sample the same population).  Sky subtraction residuals.
Model resolution and instrument resolution.  Method only useful when
you have a model for the mean spectrum?  How to interpret GP
residuals, as a fn of S/N?  Photometric upper limits? Infer the
wavelength solution as well - stellar population (and telluric lines)
as your arc. Combinations of broadening in velocity space (physical)
and in wavelength space (instrumental)

>>>>

%figures
\usepackage{graphicx}
\DeclareGraphicsExtensions{.png,.pdf}
\newcommand{\excluster}{B192-G242}

@@

We are now left to demonstrate that, by including photometry as well
as spectroscopy, it is possible to infer the parameters of interest
$\theta$ while marginalizing over the calibration parameters $\alpha$.
We will apply the methodology for spectrophotometric calibration
described above to \emph{actual, real} optical spectra of a stellar
clusters in M31.  Spectra of star clusters provide a good test case,
as they are less complex than galaxy spectra (for which it is
necessary to model the star formation history) but are by no means
trivial. In this way the key features of the calibration model and
methodology are not obscured.

@@

\begin{figure}[h!]
\includegraphics[width = \textwidth]{figures/dfig_b192-g242_020.png}
\caption{The calibrated (left) and uncalibrated (right) spectrum for
  \excluster, along with the uncertainties (bottom panel). The
  spectra are not normalized. \label{fig:data}}
\end{figure}

\begin{table}[h!]
\caption{List all the clusters, RA, Dec, photometry and individual exposures.}
\end{table}

@@

Nebular emission lines (which may arise from HII regions around the
clusters or from diffuse ionized gas) and interstellar absorption
lines are modeled as a sum of Gaussians of unknown amplitude $A_\ell$,
all of the same width $\sigma_e$ (which need not be the same as
stellar broadening $\sigma$) and with known central wavelengths
$\lambda_\ell$.  For emission lines the amplitudes are constrained to
be positive, while for interstellar absorption (e.g. Na D and Ca K)
the amplitudes are constrained to be negative. This framework can be
easily extended to include more complex models for the nebular
emission, such as allowing line dependent widths and velocities, and
using Voight profiles for the line shapes.

The final mean model is then given by 
\begin{eqnarray}\label{eq:MeanModel} 
\mu(\theta) &  = & (G_\sigma  \otimes F_{\theta^\prime})(\lambda) +
\sum_{\ell=0}^{N_\ell} S_\ell \\
S_\ell & = & \frac{A_\ell}{\sigma_e\sqrt{2\pi}} \exp(-\frac{(\lambda -
 \lambda_\ell)^2}{2\sigma_e^2})\\
\theta & \equiv & \left[ \{\theta^\prime\}, \sigma, \{A_\ell\}_{\ell=0}^{N_l},
  \sigma_e \right]
\quad ,
\end{eqnarray}
where $G_\sigma$ represents a Gaussian of unit area 
and standard deviation $\sigma$, 
$\otimes$ indicates convolution, 
and the full parameter set $\theta$ now includes
the instrumental wavelength broadening $\sigma$ 
and the dispersion $\sigma_e$ and
amplitudes $A_\ell$ of the $N_l$ nebular emission and interstellar
absorption lines.
This is the mean model which appears in equation
\ref{eq:SpectroscopicLF}.

@@

We first infer the parameters of interest $\theta$ for a calibrated
spectrum of one of the clusters, using the full YY-band photometry. In
Figure \ref{fig:inferred_spectrum} we show the spectrum resulting
from draws of the parameters $[\theta,\alpha]$ from the posterior
distribution.  This figure also shows the calibrated spectrum on which
the priors were conditioned, and several of the individual components
of the model constructed from each draw.  In Figure
\ref{fig:inferred_sed} we also show the residuals between the data
and the draws from the posterior, for both the spectra and the
photometry. In Figure \ref{fig:inferred_params} we show the
marginalized and joint PDFs for the parameters.

@@

\begin{figure}[h!]
\includegraphics[width=\textwidth]{figures/sfig_b192-g242_020_cal.png}
\caption{Spectra resulting from draws from the posterior parameter
space conditioned on the calibrated \excluster~ spectrum and
photometry.  Left: For each of 5 draws from the posterior we show from
top to bottom, three components of the model: the mean cluster
spectrum, the calibration vector, and the mean prediction of the
Gaussian process.  Right: From top to bottom, the full model ({\it
cyan}) compared to the observed, calibrated spectrum ({\it magenta}),
the ratio of the observed to the modeled spectrum, and the difference
between the observed spectrum and the modeled spectrum normalized by
the uncertainty.
\label{fig:inferred_spectrum}}
\end{figure}

\begin{figure}[h!]
\includegraphics[width=\textwidth]{figures/pfig_b192-g242_020_cal.png}
\caption{The photometric SED resulting \label{fig:inferred_sed}}
\end{figure}

@@

\begin{figure}[h!]
\includegraphics[width=\textwidth]{figures/cfig_b192-g242_020.png}
\caption{Show the calibration vector and our inference of it? \label{fig:inferred_calib}}
\end{figure}

@@

\subsection{Dependence on Photometric Data}
In this section we examine how the constraints on physical (and
calibration) parameters vary as a function of the number and type of
photometric points available.

@@

BDJ INSERT WORDS HERE.  We have demonstrated, using a sample of
stellar clusters in M31, that we can combine photometric and
spectroscopic data in a principled way to infer physical properties.
We do not resort to an arbitrary down-weighting or up-weighting of
certain data. Instead, we explicitly model our uncertain knowledge of
the spectral calibration and infer this calibration jointly with the physical
properties. For a number of applications this combination of
spectroscopy and photometry reduces the need for spectrophotometric
calibration.  Calibration information, if it exists, can be
incorporated into informative priors on the calibration parameters of the model.

Our strategy is easily extensible to more complicated models, which
include for example night sky-line emission in the spectroscopy (or
residuals from an intial sky-line subtraction), and uncertainties in
wavelength calibration.  DISCUSS MORE COMPLICATED COVARIANCE KERNELS,
MULTIPLE KERNELS, etc.  MODEL CHECKING.

@@

Limitations.  The strategy we have advocated has several limitations.
First, it requires a generative model for the spectrum of the object
of interest, and is thus ill-suited to discovery projects.  Second,
care must be taken to avoid absorbing interesting model deficiencies
into the calibration model.  Third, we have made the assumption that
the spectroscopy and the photometry are sampling the same populations.
In practice, differences between spectroscopic and photometric
apertures often mean that the photometry and the spectroscopy are sampling
slightly different physical regions.  The correct response to this
situation is to explicitly model the differences, incorporating prior
information about the spatial variation of physical properties.
Finally, this method is computationally intensive and expensive, since
we are constantly inverting largish matrices.

BDJ misc issues, collected here in case we want to address them and to
keep me from cluttering up the main text: Model resolution and
instrument resolution.  How to interpret GP residuals, as a fn of S/N?
Photometric upper limits? Infer the wavelength solution as well -
stellar population (and telluric lines) as your arc. Combinations of
broadening in velocity space (physical) and in wavelength space
(instrumental)
